Effects of Weather on Maize Yield in Kenya

### 2019-01-16 presentations/January2019/presentation4.tex
presentation

	\end{column}
	\begin{column}{0.15\textwidth}
  		$0.25^{\circ}$ grid \\ daily
	\end{column}
	\begin{column}{0.05\textwidth}
  			$\rightarrow$ \\ $\rightarrow$
	\end{column}
	\begin{column}{0.25\textwidth} 
   		county level \\  yearly
   	\end{column}
   		\begin{column}{0.4\textwidth} 
   		\end{column}
\end{columns}

@@

>>>>

	\end{column}
	\begin{column}{0.15\textwidth}
  		$0.25^{\circ}$ grid \\ daily
	\end{column}
	\begin{column}{0.05\textwidth}
  			$\rightarrow$ \\ $\rightarrow$
	\end{column}
	\begin{column}{0.25\textwidth} 
   		county level \\  yearly 
   	\end{column}
   		\begin{column}{0.4\textwidth} 
   		\end{column}
\end{columns}
\textcolor{red}{add how averaged over seasons ASAL and non ASAL}

@@

\begin{frame}\label{measures} 
\small
\frametitle{Precipitation and temperature measures}
\begin{itemize}
\item Measures typically considered:

	\begin{itemize}
		\item Total precipitation over rainy seasons
		\item Average temperature during rainy seasons
		\item Average maximum daily temperature during rainy seasons
	\end{itemize}

\item{Less commonly used measures considered:}
	\begin{itemize}
		\item Coefficients of variation: precipitation and temperature
		\item Maximum length of dry spell during rainy seasons
		\item Number of dry spells during rainy seasons
		\item Cumulative degree days over rainy seasons
		\item Number of heatwave days
		\item Cumulative precipitation on days when precip. $>90th$ percentile
	\end{itemize}

\note{dry day defined when temperature below 1mm\\various definitions of dry spell (5days, 10days, 20days)\\ degree days between 10 and 30C\\ heatwave days above 35C}
%oooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooo
%oooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooo

\frametitle{ideas}
\color{red}
\begin{itemize}
\item Plot of dependency of precip or some measure and yields..

\end{itemize}
\color{black}
\end{frame}
